Native advertising as a content marketing strategy

### 2024-09-10 analysis/paper/paper.Rmd
weiter

•	Application area: Is native advertising a public relations technique, a marketing tool, or a tactic that does not differ from traditional advertising in any way?
•	Authorship of native ads: Who creatively signs them and who is responsible for their content?
•	Legal and ethical framework: How is native advertising legally defined, and what is the practice of media houses in labelling such advertisements (Trbušić, Maleš & Šikić, 2024).

>>>>

>	Application area: Is native advertising a public relations technique, a marketing tool, or a tactic that does not differ from traditional advertising in any way?

>	Authorship of native ads: Who creatively signs them and who is responsible for their content?

>	Legal and ethical framework: How is native advertising legally defined, and what is the practice of media houses in labelling such advertisements (Trbušić, Maleš & Šikić, 2024).
